Music Perception 2020: Stimuli profiles (3sd)

### 2020-10-12 material/stimuli/R/analysis/3sd.Rmd
analysis for 3sd data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Music Perception 2020: Stimuli profiles (random)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

I chose stimuli randomly.  
Note: SubNr16 was excluded because of a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))

@@

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../random/art_teaching", pattern = "txt")
lf_a_p <- list.files("../random/art_performing", pattern = "txt")
lf_d_t <- list.files("../random/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../random/dyn_performing", pattern = "txt")

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../random/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../random/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../random/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../random/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}

>>>>

---
title: 'Music Perception 2020: Stimuli profiles (3sd)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

I chose stimuli with the IOIs within 3SD randomly.  
Note: SubNr16 was excluded because of a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))

@@

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../3sd/art_teaching", pattern = "txt")
lf_a_p <- list.files("../3sd/art_performing", pattern = "txt")
lf_d_t <- list.files("../3sd/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../3sd/dyn_performing", pattern = "txt")

# merge all data files into one
data <- data.table()
for (i in 1:length(lf_a_t)){
  data_i <- fread(file.path("../3sd/art_teaching", lf_a_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_a_p)){
  data_i <- fread(file.path("../3sd/art_performing", lf_a_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_t)){
  data_i <- fread(file.path("../3sd/dyn_teaching", lf_d_t[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
for (i in 1:length(lf_d_p)){
  data_i <- fread(file.path("../3sd/dyn_performing", lf_d_p[i]), header = T, sep = ",", dec = ".")
  data_i$Instance <- i
  data <- rbind(data, data_i)
}
